---
title: "Macy's Revenue Prediction"
author: "Yiyang Duanmu"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import packages and data

```{r}
library(forecast)
library(zoo)
library(ggplot2)
library(astsa)
library(patchwork)

macy <- read.csv("~/Downloads/MacyRevenue.csv")
ama <- read.csv("~/Downloads/AmazonRevenue.csv")
ur <- read.csv("~/Downloads/QuarterlyUR.csv")
gdpg <- read.csv("~/Downloads/GDPGrowthRate.csv")

macy.ts <- ts(macy$Revenue, start = c(2008,4), end = c(2022,2), frequency = 4)
ama.ts <- ts(ama$Revenue, start = c(2009,1), end = c(2022,2), frequency = 4)
ur.ts <- ts(ur$UR, start = c(2008,4), end = c(2022,2), frequency = 4)
gdpg.ts <- ts(gdpg$GDP.Growth.Rate, start = c(2008,4), end = c(2022,2), frequency = 4)
```

# Split data set

```{r}
n <- length(macy.ts)
stepsAhead <- 10
nTrain <- n-stepsAhead

train.m.ts <- window(macy.ts, end = c(2019,4), frequency = 4)
valid.m.ts <- window(macy.ts, start = c(2020,1), frequency = 4)
```

# Navie Forecast

```{r}
naive <- naive(train.m.ts,h = 10)
snaive <- snaive(train.m.ts,h = 10)
accuracy(naive, valid.m.ts)
accuracy(snaive, valid.m.ts)

autoplot(train.m.ts, ylab="Macy's Revenue", main = "Naive & Seasonal Naive Forecast")+
  autolayer(valid.m.ts, series = "Observed")+
  autolayer(naive, series = "Naive", PI=F,lwd = 0.8)+
  autolayer(snaive, series = "Seasonal Naive",PI=F,lwd = 0.8)

checkresiduals(naive)
checkresiduals(snaive)
```

# Moving average smoothing: centered and trailing

```{r}
# center, roll mean
ma.centered <- ma(macy.ts, order = 4, centre = T) # centered
w <- 4

ma.trailing <- rollmean(train.m.ts, k = w, align = "right") # mean
ma.trailing.max<- rollmax(train.m.ts, k = w, align = "right") # max
ma.trailing.median <- rollmedian(train.m.ts, k = 5, align = "right") # median
ma.trailing.sum<- rollsum(train.m.ts, k = w, aligh="right") # sum

autoplot(macy.ts, ylab="Revenue", series = "Observed")+
  autolayer(ma.centered, series = "Moving Average Centered", lwd=1.5)+
  autolayer(ma.trailing, series = "Moving Mean", lwd=1.5)+
  autolayer(ma.trailing.median, series = "Moving Median", lwd=1.5)+
  autolayer(ma.trailing.max, series = "Moving Max", lwd=1.5)

# One Step Ahead Rolling Forecast(rollmean)

last.ma <- tail(ma.trailing, 1)

ma.trailing.pred <- ts(rep(last.ma, stepsAhead),
                       start = c(2020,1),
                       end = c(2022,2),frequency =4)
# actual
valid.mean = ts(rep(mean(valid.m.ts), stepsAhead),
                start = c(2020, 1),
                end = c(2022, 2),
                frequency = 4)

# looping
ma.trailing.pred.rolling.mean <- rep(NA, stepsAhead)

start.year = 2008
w <- 10
for(i in 1:stepsAhead){
  #i = 1
  nTrain <- n - stepsAhead + (i-1)
  train.ts <- window(macy.ts,start=c(2008,4),end=c(start.year, nTrain+3))
  ma.trailing.mean = rollmean(train.ts, k = w, align = "right")
  # our long term forecast
  last.ma.mean <- tail(ma.trailing.mean, 1)
  ma.trailing.pred.rolling.mean[i] <- last.ma.mean
}

ma.roll.ts.mean <- ts(ma.trailing.pred.rolling.mean, 
                 start = c(2020, 1), frequency = 4)

autoplot(macy.ts, ylab="Macy's Revenue")+
  autolayer(ma.trailing, series = "Fitted", lwd = 1.5)+
  autolayer(ma.trailing.pred, series = "Predicted", lwd=1.5)+
  autolayer(valid.mean, series="Actual mean", lwd=1.5)+
  autolayer(ma.roll.ts.mean, series ="Rolling Mean",lwd=1.5)

# One Step Ahead Rolling Forecast(Rollmedian)

nValid = 10
ma.trailing.pred.rolling.median <- rep(NA, stepsAhead)

for(i in 1:nValid){
  nTrain <- n - nValid + (i-1)
  train.ts<-window(macy.ts,start=c(2008,4),end=c(start.year, nTrain+3))
  ma.trailing.roll.median <- rollmedian(train.ts, k = 11, align = "right") 
  # k=9/11 is same accuracy
  last.ma.median = tail(ma.trailing.roll.median, 1)
  ma.trailing.pred.rolling.median[i]=last.ma.median
}

ma.roll.median.ts <- ts(ma.trailing.pred.rolling.median, 
                 start = c(2020,1), frequency = 4)

autoplot(macy.ts, ylab="Macy's Revenue", main = "Moving Average")+
  autolayer(ma.trailing, series = "Fitted", lwd = 0.8)+
  autolayer(ma.trailing.pred, series = "Predicted", lwd=0.8)+
  autolayer(ma.roll.ts.mean, series ="Rolling Mean",lwd=0.8)+
  autolayer(ma.roll.median.ts, series ="Rolling Median",lwd=0.8)

# Accuracy

accuracy(ma.roll.ts.mean,valid.m.ts)
accuracy(ma.roll.median.ts,valid.m.ts)
```

# Exponential Smoothing

```{r}
aan <- ets(train.m.ts, model = 'AAN')
ann <- ets(train.m.ts, model = 'ANN')
aaa <- ets(train.m.ts, model = 'AAA')
zzz <- ets(train.m.ts, model='ZZZ') # mna <- ets(train.m.ts, model = 'MNA')

aan.predict <- forecast.ets(aan, h=10, level=0)
ann.predict <- forecast.ets(ann, h=10, level=0)
aaa.predict <- forecast.ets(aaa, h=10, level=0)
zzz.predict <- forecast.ets(zzz, h=10, level=0)

accuracy(aan.predict, valid.m.ts)
accuracy(ann.predict, valid.m.ts)
accuracy(aaa.predict, valid.m.ts)
accuracy(zzz.predict, valid.m.ts) # Best "MNA"

autoplot(train.m.ts,  ylab = 'Revenue',xlab = 'Time', main = 'Forecast Macy Revenue (Exponential Smoothing)')+
  autolayer(valid.m.ts, series = 'Validation')+
  autolayer(aan.predict, series='AAN predicted')+
  autolayer(ann.predict, series='ANN predicted')+
  autolayer(aaa.predict, series='AAA predicted')+
  autolayer(zzz.predict, series='ZZZ predicted',lwd=1)
```

# Arima

```{r}
# Try Detrend and Deseasonality

#(1) Detrend and Deseasonality
ddtrain<-diff(diff(train.m.ts,1),4)
par(mfrow=c(1,2))
Acf(ddtrain,36,main="")
Pacf(ddtrain,36, main="")
par(mfrow=c(1,1))

#(2) Detrend
dttrain<-diff(train.m.ts,1)
par(mfrow=c(1,2))
Acf(dttrain,36,main="ACF Plot")
Pacf(dttrain,36, main="PACF Plot")
par(mfrow=c(1,1))

#(3) Deseasonality
dstrain<-diff(train.m.ts,4)
par(mfrow=c(1,2))
Acf(dstrain,36,main="")
Pacf(dstrain,36, main="")
par(mfrow=c(1,1))

# ACF tailing off and PACF cutting off. Therefore, choose AR model. Look at PACF, choose 1. 

# model 1
am1 <- Arima(train.m.ts, order = c(1,1,1), seasonal = list(order = c(1,1,0), period = 4))
summary(am1)
am1.predict <- forecast(am1, h = 10, level = 0)
autoplot(am1.predict)
autoplot(valid.m.ts)+
  autolayer(am1.predict)
accuracy(am1.predict, valid.m.ts)
checkresiduals(am1)

# model 2
am2 <- Arima(train.m.ts, order = c(2,0,1), seasonal = list(order = c(1,0,0), period = 4))
summary(am2)
am2.predict <- forecast(am2, h = 10, level = 0)
autoplot(valid.m.ts)+
  autolayer(am2.predict)
accuracy(am2.predict, valid.m.ts)
checkresiduals(am2)
```

# External Factors: Unemployment Rate, GDP Growth Rate (Inflation-adjusted)

## Correlation Coefficient Value

```{r}
sa <- rollmean(macy.ts, k = 4, align = "right")
newmacy <- ts.intersect(SA_M = sa, UR = ur.ts, GDPG = gdpg.ts)
cor(x = newmacy[,2], y = newmacy[,1]) # UR
cor(x = newmacy[,3], y = newmacy[,1]) # GDPG
```

## Split Data Set

```{r}
train.g.ts <- window(gdpg.ts, end = c(2019,4), frequency = 4)
valid.g.ts <- window(gdpg.ts, start = c(2020,1), frequency = 4)

train.u.ts <- window(ur.ts, end = c(2019,4), frequency = 4)
valid.u.ts <- window(ur.ts, start = c(2020,1), frequency = 4)
```

## Time Series Linear Regression Models

```{r}
lm1 <- tslm(train.m.ts ~ trend + season + train.g.ts)
summary(lm1) # R square: 0.9443
lm1.pred <- forecast(lm1, data.frame(train.g.ts = valid.g.ts))
accuracy(lm1.pred, valid.m.ts)
autoplot(macy.ts, main = "lmcay ~ trend + season + gdp growth rate")+
  autolayer(lm1$fitted.values)+
  autolayer(lm1.pred$mean)

lm2 <- tslm(train.m.ts ~ trend + season + train.u.ts)
summary(lm2) # R square: 0.9275
lm2.pred <- forecast(lm2, data.frame(train.u.ts = valid.u.ts))
accuracy(lm2.pred, valid.m.ts)
autoplot(macy.ts, main = "lmcay ~ trend + season + gdp growth rate + unemployment rate")+
  autolayer(lm2$fitted.values)+
  autolayer(lm2.pred$mean)

lm3 <- tslm(train.m.ts ~ trend + season + train.g.ts + train.u.ts)
summary(lm3) # R square: 0.9478
lm3.pred <- forecast(lm3, data.frame(train.g.ts = valid.g.ts, train.u.ts = valid.u.ts))
accuracy(lm3.pred,valid.m.ts) # Best, Lowest MAPE: 12.56
autoplot(macy.ts, ylab = "Macy's Revenue",main = "Macy Revenue ~ trend + season + GDP growth rate + Unemployment rate")+
  autolayer(lm3.pred$mean, series = "Predicted", lwd = 0.8)+
  autolayer(lm3$fitted.values, series = "Fitted")

# checkresiduals(lm3)
```

## ArimaX

```{r}
axm1 <- Arima(train.m.ts,order = c(2,0,1),seasonal = list(order = c(1,1,0),period = 4),xreg = train.g.ts)
summary(axm1)
arimax.pred <- forecast(axm1, h =10, xreg = valid.g.ts)$mean
accuracy(arimax.pred, valid.m.ts)
autoplot(macy.ts)+
  autolayer(arimax.pred)

axm2 <- Arima(train.m.ts,order = c(2,0,1),seasonal = list(order = c(1,1,0),period = 4),xreg = train.u.ts)
summary(axm2)
arimax.pred <- forecast(axm2, h =10, xreg = valid.u.ts)$mean
accuracy(arimax.pred, valid.m.ts)
autoplot(macy.ts)+
  autolayer(arimax.pred)

axm3 <- Arima(train.m.ts,order = c(2,0,1),seasonal = list(order = c(1,1,0),period = 4),xreg = cbind(train.u.ts,train.g.ts))
summary(axm3)
arimax.pred <- forecast(axm3, h =10, xreg = cbind(train.u.ts = valid.u.ts,train.g.ts = valid.g.ts))$mean
accuracy(arimax.pred, valid.m.ts)
autoplot(macy.ts,ylab = "Macy's Revenue", main = "ARIMAX(2,0,1)(1,1,0)[4](GDP growth rate,Unemployment rate)")+
  autolayer(axm3$fitted, series = "ARIMAX Fitted" )+
  autolayer(arimax.pred, series = "ARIMAX Predicted", lwd = 0.8 )
```

# Competitor Analysis: Amazon

## Split Data Set

```{r}
gdpg.ts <- window(gdpg.ts,start = c(2009,1), frequency = 4)
ur.ts <- window(ur.ts, start =c(2009,1), frequency = 4)

train.a.ts <- window(ama.ts, end = c(2019,4), frequency = 4)
valid.a.ts <- window(ama.ts, start = c(2020,1), frequency = 4)

train.g.ts <- window(gdpg.ts, end = c(2019,4), frequency = 4)
valid.g.ts <- window(gdpg.ts, start = c(2020,1), frequency = 4)

train.u.ts <- window(ur.ts, end = c(2019,4), frequency = 4)
valid.u.ts <- window(ur.ts, start = c(2020,1), frequency = 4)
```

## Arima

```{r}
#(1) Detrend and Deseasonality
ddtrain<-diff(diff(train.a.ts,1),4)
par(mfrow=c(1,2))
Acf(ddtrain,36,main="")
Pacf(ddtrain,36, main="")
par(mfrow=c(1,1))

#(2) Detrend
dttrain<-diff(train.a.ts,1)
par(mfrow=c(1,2))
Acf(dttrain,36,main="ACF Plot")
Pacf(dttrain,36, main="PACF Plot")
par(mfrow=c(1,1))

#(3) Deseasonality
dstrain<-diff(train.a.ts,4)
par(mfrow=c(1,2))
Acf(dstrain,36,main="")
Pacf(dstrain,36, main="")
par(mfrow=c(1,1))

aam <- Arima(train.a.ts, order = c(1,1,0), seasonal = list(order=c(1,1,0),period=4))
aam.predict <- forecast(aam, h = 10,level = 0)
autoplot(valid.a.ts)+
  autolayer(aam.predict)
accuracy(aam.predict,valid.a.ts)
checkresiduals(aam)
```

## External Factors: Unemployment Rate, GDP Growth Rate (Inflation-adjusted)

```{r}
# Correlation Coefficient Value

sa.ama <- rollmean(ama.ts, k = 4, align = "right")
newama <- ts.intersect(SA_M = sa.ama, UR = ur.ts, GDPG = gdpg.ts)

cor(x = newama[,2], y = newama[,1]) # -0.4943394
cor(x = newama[,3], y = newama[,1]) # 0.1152857

# Linear Regression

alm1 <- tslm(train.a.ts ~ trend + season + train.g.ts)
alm1.pred <- forecast(alm1, data.frame(train.g.ts = valid.g.ts))
accuracy(alm1.pred,valid.a.ts)
autoplot(ama.ts, main = "Amazon Revenue ~ trend + season + GDP growth rate")+
  autolayer(alm1$fitted.values)+
  autolayer(alm1.pred$mean)

alm2 <- tslm(train.a.ts ~ trend + season + train.u.ts)
summary(alm2) # 0.9485
alm2.pred <- forecast(alm2, data.frame(train.u.ts = valid.u.ts))
accuracy(alm2.pred,valid.a.ts)
almp2 <- autoplot(ama.ts, ylab="Amazon Revenue", main = "Revenue ~ Unemployment rate")+
  autolayer(alm2$fitted.values, series = "Fitted")+
  autolayer(alm2.pred$mean, series = "Predicted", lwd = 0.8)+ theme(legend.position = c(0.25, 0.8))

alm3 <- tslm(train.a.ts ~ trend + season + train.g.ts + train.u.ts)
alm3.pred <- forecast(alm3, data.frame(train.u.ts = valid.u.ts, train.g.ts = valid.g.ts))
accuracy(alm3.pred,valid.a.ts)
almp3 <- autoplot(ama.ts, ylab="Amazon Revenue", main = "Revenue ~ GDP growth rate + Unemployment rate")+
  autolayer(alm3$fitted.values, series = "Fitted")+
  autolayer(alm3.pred$mean, series = "Predicted", lwd = 0.8)+ theme(legend.position = c(0.25, 0.8))

almp2 + almp3

# ArimaX

aaxm1 <- Arima(train.a.ts,order = c(1,1,0),seasonal = list(order = c(1,1,0),period = 4),xreg = train.g.ts)
summary(aaxm1)
arimax.pred <- forecast(aaxm1, h =10, xreg = valid.g.ts)$mean
accuracy(arimax.pred, valid.a.ts)
autoplot(ama.ts, ylab = "Amazon Revenue", main = "ARIMAX(1,1,0)(1,1,0)[4](GDP Growth Rate)")+
  autolayer(aaxm1$fitted, series = "ARIMAX Fitted")+
  autolayer(arimax.pred, series = "ARIMAX Predicted", lwd = 0.8)

aaxm2 <- Arima(train.a.ts,order = c(1,1,0),seasonal = list(order = c(1,1,0),period = 4),xreg = train.u.ts)
summary(aaxm2)
arimax.pred <- forecast(aaxm2, h =10, xreg = valid.u.ts)$mean
accuracy(arimax.pred, valid.a.ts)
autoplot(ama.ts, ylab = "Amazon Revenue", main = "ARIMAX(1,1,0)(1,1,0)[4](Unemployment Rate)")+
  autolayer(aaxm2$fitted, series = "ARIMAX Fitted")+
  autolayer(arimax.pred, series = "ARIMAX Predicted", lwd = 0.8)

aaxm3 <- Arima(train.a.ts,order = c(1,1,0),seasonal = list(order = c(1,1,0),period = 4),xreg = cbind(train.u.ts,train.g.ts))
summary(aaxm3)
arimax.pred <- forecast(aaxm3, h =10, xreg = cbind(train.u.ts = valid.u.ts,train.g.ts = valid.g.ts))$mean
accuracy(arimax.pred, valid.a.ts)
autoplot(ama.ts, ylab = "Amazon Revenue", main = "ARIMAX(1,1,0)(1,1,0)[4](GDP Growth Rate + Unemployment Rate)")+
  autolayer(aaxm3$fitted, series = "ARIMAX Fitted")+
  autolayer(arimax.pred, series = "ARIMAX Predicted", lwd = 0.8)
```



